What do incoming university students believe about open science practices in

### 2021-02-11 analysis/Manuscript.Rmd
preprocessing/*.R

# all participants
n_all <- nrow(df)

# note re: exclusion
# exclude those who are younger than 18
# only those who say "1" to eligibility are included; all other responses are excluded
# those whose `status` variable is an 'IP Address' are included

age <- df %>%
  dplyr::count(age_lab)

el <- df %>%
  dplyr::count(eligibility_lab)

status <- df %>% 
  dplyr::count(status_lab)

# n <- el[5,2] [need to specify a final n : Breadcrumbs]

@@

Of those who started the survey (*n* = `r n_all`), we screened out participants who 
were not eligible to participate based on our preregistration. Specifically, 
we screened out people who were younger than 18 years of age (*n* = `r age[1,2]`). 
We also screened out individuals who had already started a psychology unit at a
university, regardless of whether they completed it (*n* = `r el[1,2] + el[3,2] + el[4,2]`); 
were not enrolled in a psychology unit at a university (*n* = `r el[2,2]`); or did 
not answer this question (*n* = `r el[6,2]`). The remaining `r el[5,2]` participants
were eligible based on starting their first unit of study in psychology at 
a university within the next month. For those individuals who were screened out, 
our Qualtrics program automatically directed them to the debriefing form.

Of the remaining `r n` participants, most reported that they were
18-24 years old (*n* = `r age[2,2]`), `r age [3,2]` 
reported that they were 25-34 years old, `r age [4,2]` were 35-44 years old,
`r age [5,2]` were 45-54 years old, `r age [6,2]` were 55-64 years old, and
`r age [7,2]` were 65 years or older. A small number of participants did not 
report their age(*n* = `r age [8,2]`).

>>>>

# participant numbers (all & included cases)
df_all <- df
n_all <- nrow(df_all)
df <- df_all %>% 
  filter(exclude %in% "include") # only those who met the inclusion criterion
n <- nrow(df)

ex <- df_all %>% 
  filter(exclude %in% "exclude") %>% # n for those excluded
  nrow()

# note re: exclusion [all coded in `exclude` in preprocessing, 
# but need to summarise exclusion criteria here]
  # exclude those who are younger than 18
  # only those who say "1" to eligibility are included; all other responses are excluded
  # those whose `status` variable is an 'IP Address' are included

age <- df_all %>%
  dplyr::count(age_lab)

el <- df_all %>%
  dplyr::count(eligibility_lab)

status <- df_all %>% 
  dplyr::count(status_lab)

@@

Of those who started the survey (*n* = `r n_all`), we screened out `r ex` 
participants who were not eligible to participate based on the combination of our
preregistered exclusion criteria. Specifically, we screened out people who were younger than 
18 years (*n* = `r age[1,2]`). We also screened out individuals who had already 
started a psychology unit at a university, regardless of whether they had 
completed it (*n* = `r el[1,2] + el[3,2] + el[4,2]`); were not enrolled in a 
psychology unit at a university (*n* = `r el[2,2]`); or did not answer this 
question (*n* = `r el[6,2]`). We also screened out an additional XX participants
who met our eligibility criteria, but did not respond to any of the main items
in the study.

The remaining `r n` participants
were eligible based on starting their first unit of study in psychology at 
a university within the next month. For those individuals who were screened out, 
our Qualtrics program automatically directed them to the debriefing form.

Of the remaining `r n` participants, most reported that they were
18-24 years old (*n* = `r age[2,2]`), `r age [3,2]` 
reported that they were 25-34 years old, `r age [4,2]` were 35-44 years old,
`r age [5,2]` were 45-54 years old, `r age [6,2]` were 55-64 years old, and
`r age [7,2]` were 65 years or older.
